We have presented a general robust self-testing theorem for a certain class of linear constraint system games, using the group-theoretic approach of Cleve, Liu and Slofstra. We specialized this theorem to the cases of the Magic Square and Magic Pentagram games mod $2$, obtaining robust self-testing theorems for respectively two and three pairs of maximally entangled qubits and the associated ideal measurements. Furthermore, we applied our theorem to a certain $n$-fold product of these games to obtain a robust self-testing theorem for a tensor product of $n$ maximally entangled qubits and the associated $n$-qubit Pauli measurements. The following are some remaining open questions.

\begin{question}
	For which $d$ is there a non-local game self-testing the maximally entangled state of local dimension $d$?
\end{question}
In \cite{coladangelo2018generalization}, one of us gave a family of Bell inequalities whose maximal violation self-tests the maximally entangled game of local dimension $d$ for any $d > 2$. However, this translates into non-local games which are not pseudotelepathy (i.e. they do not have a perfect strategy). 
If one considers just pseudotelepathy games, it is known that there are no non-local games which can be won perfectly with dimension $2$ but not with dimension $1$ (i.e.\ with a classical strategy) \cite{brassard2004minimum}; this answers the above question in the negative for $d=2$. For $d=3$, there is a pseudotelepathy game based on Kochen-Specker sets for which there is no classical perfect strategy and there is a perfect quantum strategy using the maximally entangled state of qutrits. \cite{cleve2004consequences} To the best of the authors' knowledge, the question of rigidity is open for this game.

Restricting our attention to just to LCS games, we can reduce the above question to the following:
\begin{question}
	For any $d$, is there a solution group $\G$ presented over $\Z_d$ such that every irreducible representation of $\G$ is either $1$-dimensional or $d$-dimensional, sending $J$ to a nontrivial $d\th$ root of unity? 
\end{question}
$\m P_d^{\otimes 1}$ has this property, but it can be shown that it is not a solution group. 
Classifying the groups with the above property seems like a nontrivial question in group theory.

The following question represents, in the authors' opinion, the main barrier to understanding the full power of general LCS games.
\begin{question}
	Which groups are solution groups? In particular, are there any nonabelian finite solution groups other than the groups of qubit paulis?
\end{question}
William Slofstra gave a partial answer to this question by proving \emph{embedding theorems.} First, he proved \cite{slofstra2016tsirelson} that all finitely presented groups embed into some solution group over $\Z_2$. Next, he proved \cite{slofstra2017set} that a somewhat broad class of groups, including all finite symmetric groups, embed into binary solution groups such that the embedding preserves the finite-dimensional approximate representation structure. These embeddings fail to preserve finiteness of the group, however.


