\documentclass{article}
\usepackage{JalexMath}
\usepackage{authblk}
\usepackage[toc,page]{appendix}
\usepackage{rotating}
\usepackage{caption}
\usepackage[margin=1in]{geometry}
\usepackage[showonlyrefs]{mathtools}
% \input{header/tikz_header}

\bibliographystyle{alpha}

\pagestyle{headings}

\mathtoolsset{showonlyrefs=true} % turns off equation number for un-referenced equations

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup}


\newcommand\jnote[1]{
\begin{footnotesize}
	\color{green}{(Jalex: #1)}
\end{footnotesize}
}
\newcommand\anote[1]{
\begin{footnotesize}
	\color{blue}{(Andrea: #1)}
\end{footnotesize}
}


\newcommand{\dagg}{^\dagger}
\newcommand{\eps}{\e}
\newcommand{\eprp}{\ket{\r{EPR}_d}}
\newcommand{\epr}{{\r{EPR}_d}}
\newcommand{\hatA}[2]{\hat A_{#1}^{(#2)}}
\newcommand{\eprrho}{{\r{EPR}_\s}}
\newcommand{\pauli}{\m P_d^{\otimes n}}
\newcommand{\paulin}[1]{\m P_d^{\otimes #1}}
\newcommand{\drho}[3]{\mathop{D}\limits_{#1}\left(#2\middle\| #3\right)}

\newcommand\todo[1]{{\color{red}{(TODO: #1)}}}

\complexity{LCS}
\DeclareMathOperator*\can{\sf{can}}


\begin{document}
\title{Robust self-testing for linear constraint system games}

\author{Andrea Coladangelo}
\author{Jalex Stark}
\date{}
\affil{
% Department of 
Computing and Mathematical Sciences, Caltech\\ 
{\{acoladan,jalex\}@caltech.edu}
}
% \affil[ ]{{ }}
\maketitle

\abstract{
	We study linear constraint system (LCS) games over the ring of arithmetic modulo $d$. 
    We give a new proof that certain LCS games (the Mermin--Peres Magic Square and Magic Pentagram over binary alphabets, together with parallel repetitions of these) have unique winning strategies, where the uniqueness is robust to small perturbations.
	In order to prove our result, we extend the representation-theoretic framework of Cleve, Liu, and Slofstra \cite{cleve2016perfect} to apply to linear constraint games over $\Z_d$ for $d\geq 2$. We package our main argument into machinery which applies to any nonabelian finite group with a ``solution group'' presentation. We equip the $n$-qubit Pauli group for $n\geq 2$ with such a presentation; our machinery produces the Magic Square and Pentagram games from the presentation and provides robust self-testing bounds.
	The question of whether there exist LCS games self-testing maximally entangled states of local dimension not a power of 2 is left open. A previous version of this paper falsely claimed to show self-testing results for a certain generalization of the Magic Square and Pentagram mod $d\neq 2$. We show instead that such a result is impossible.
}

\pagenumbering{gobble}
\pagebreak
\pagenumbering{arabic}

\tocless\section{Introduction}
	\input{introduction.tex}


\section*{Acknowledgements}

An early version of Theorem \ref{thm:informal-magic-square} used a more complicated linear constraint game. We thank William Slofstra for pointing out that the same analysis goes through for the Magic Square.

The arxiv version 1 of this paper falsely claimed that in a certain $3\times 3$ square of operators, every pair of operators sharing a row or column commute. We thank Richard Cleve, Nadish De Silva and Joel Wallman for pointing out that one pair of them did not. 
We thank Richard Cleve and Joel Wallman for sharing with the authors a proof that the magic square game mod $d$ for $d\neq 2$ is not a pseudotelepathy game. More details about this impossibility are provided in section \ref{sec:impossibility}.

We thank 
William Ballinger,
William Hoza,
Jenish Mehta,
Chinmay Nirkhe,
William Slofstra,
Thomas Vidick,
Matthew Weidner,
and
Felix Weilacher
for helpful discussions.
We thank Martino Lupini for pointing us to reference \cite{de2017operator} and Scott Aaronson for pointing us to reference \cite{cleve2004consequences}.

We thank
Arjun Bose,
Chinmay Nirkhe, 
and 
Thomas Vidick
for helpful comments on preliminary drafts of the paper.

We thank Thomas Vidick for various forms of guidance throughout the project. A.C. was supported by AFOSR YIP award number FA9550-16-1-0495.
J.S. was supported by NSF CAREER Grant CCF-1553477 and the Mellon Mays Undergraduate Fellowship. 
Part of this work was completed while J.S. was visiting UT Austin. 

\tableofcontents


\section{Preliminaries}\label{sec:preliminaries}
	\input{preliminaries.tex}

\section{Linear constraint system games over $\Z_d$}\label{sec:linear-constraint-games}
	\input{linear-constraint-games.tex}

\section{General self-testing}\label{sec:self-testing}
	\input{self-testing.tex}

\section{On the failure of Magic Square and Pentagram for $d\neq 2$}\label{sec:impossibility}
	\input{impossibility.tex}
	
\section{Self-testing of specific games}\label{sec:specific-games}
	\input{specific-games.tex}
	


\section{Concluding remarks}
\input{conclusion.tex}

% \printbibliography

\bibliography{ms}

\input{appendix.tex}

\end{document}